\chapter*{Acknowledgements}\markboth{Acknowledgements}{Acknowledgements}

This HOL Light Reference manual is derived from the original {\REFERENCE}
document for the HOL88 system, and generates the main body from online help
entries in the same way and using essentially the same scripts. Many of these
entries are minor edits of HOL88 originals, though plenty are also completely
new. All in the latter group (and some of the former) were written by John
Harrison. The re-use of the existing infrastructure was suggested by Steve 
Brackin.

The original HOL88 documentation project was managed by Mike Gordon at the
Cambridge (UK) Research Center of SRI International, with the support of DSTO
Australia. The main reference entries were written in a joint effort by members
of the Cambridge {\HOL} group. The original document design used \LaTeX\ macros
supplied by Elsa Gunter, Tom Melham and Larry Paulson.  The typesetting of all
three volumes was managed by Tom Melham. The conversion of the {\tt troff}
sources of {\sl The ML Handbook\/} to \LaTeX\ was done by Inder Dhingra and
John Van Tassel. The cover design is by Arnold Smith, who used a photograph of
a `snow watching lantern' taken by Avra Cohn (in whose garden the original
object resides). John Van Tassel composed the \LaTeX\ picture of the lantern.

Many people other than those listed above have contributed to the {\HOL}
documentation effort, either by providing material, or by sending lists of
errors in the first edition.  Thanks to everyone who helped, and thanks to DSTO
and SRI for their generous support.
