\chapter*{Preface}\markboth{Preface}{Preface}

This volume is the reference manual for the HOL Light system. In contrast to
the Tutorial, it is mainly intended for reference purposes, though some readers
will find it productive to browse through it as part of the learning process.
The main entries for the reference manual are generated from the same database
that is used by the online HOL Light help system.

The entries that follow provide documentation on essentially all the
pre-defined {\ML} variable bindings in the HOL Light system. These include:
general-purpose functions, such as ML functions for list processing,
arithmetic, input/output, and interface configuration; functions for processing
the types and terms of the {\HOL} logic and for using the subgoal package;
primitive and derived forward inference rules; tactics and tacticals; and
pre-proved built-in theorems.

The manual entries for these {\ML} identifiers are divided into two chapters.
The first chapter is an alphabetical sequence of manual entries for all {\ML}
identifiers in the system except those identifiers that are bound to theorems
(or pairs of theorems, etc.) The theorems are listed in the second chapter,
roughly grouped into sections based on subject matter.

Our documentation does not cover basic functions in the OCaml toplevel, such as
addition, string concatenation etc. In fact, relatively few native OCaml
functions are used, and those are all documented in the Objective CAML
Reference Manual:

\url{http://caml.inria.fr/pub/docs/manual-ocaml/index.html}
